Global code motion of congruent instructions

### 2017-04-18 paper.tex
code size comments

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|c|c|}
      \hline
% TODO: Check if putting code-size or spills number is okay or only %age is required.
% llvm trunk vs. llvm trunk with code-motion
                &\% performance uplift & \% code size decrease & \% code size decrease\\
Benchmarks      & at -Ofast (high better)& at -Ofast (high better) & at -Os (high better)\\\hline
400.perlbench	& 1.00  & -9120  & 544.00  \\\hline
401.bzip2	& 1.00  & -1600  & 128.00  \\\hline
403.gcc	        & 1.00  & -58176 & 3384.00 \\\hline
429.mcf	        & 1.03  & 160    & 16.00   \\\hline
433.milc	& 1.00  & -656   & 224.00  \\\hline
444.namd	& 1.00  & -3864  & -1168.00\\\hline
445.gobmk	& 0.99  & -20480 & -264.00 \\\hline
447.dealII	& 0.95  & -27836 & 50934.00\\\hline
450.soplex	& 0.99  & 2220   & 348.00  \\\hline
453.povray	& 0.97  & 164    & -472.00 \\\hline
456.hmmer	& 0.99  & -3464  & -352.00 \\\hline
458.sjeng	& 1.02  & 440    & 1456.00 \\\hline
462.libquantum	& 1.00  & -96    & 0.00    \\\hline
464.h264ref	& 1.00  & -3424  & 864.00  \\\hline
470.lbm	        & 1.00  & 0      & 0.00    \\\hline
471.omnetpp	& 1.00  & 2688   & 200.00  \\\hline
473.astar	& 1.00  & -928   & 152.00  \\\hline
482.sphinx3	& 0.99  & 3008   & -176.00 \\\hline
483.xalancbmk	& 1.01  & 46492  & 4012.00 \\\hline
Geomean         & 0.997 &  & \\\hline
    \end{tabular}
  \end{center}
  \caption{Execution time and code size with and without \gcm{}
    (\GCM{}) on \SPEC{}: performance uplift at -Ofast in mcf and sjeng; code size
    improvement in dealII at -Os.}
  \label{tab:code-size}
\end{table}

@@

Code size also remained almost the same as a result of \gcm{} as shown in
Table~\ref{tab:code-size}.  The code size listed here is the text size (from
linux size command) of the final executable for each benchmark.  Some benchmarks
like 473.astar increased in code size by almost 2\%. This is because once the
code-size of a function decreases (due to \GCM{}), it becomes cheaper to
inline. As we can see in Table~\ref{tab:stats}, four more functions got inlined
in 473.astar. Except for 447.dealII, 450.soplex, 482.sphinx3 and 483.xalancbmk
all other benchmarks got more functions inlined. Also, since the pass runs
early, it affects many optimizations which rely on the number of instructions,
length of the use-def chain, and other metrics.

>>>>

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|c|c|}
      \hline
% TODO: Check if putting code-size or spills number is okay or only %age is required.
% llvm trunk vs. llvm trunk with code-motion
                &\% performance uplift & \% code size decrease & \% code size decrease\\
Benchmarks      & at -Ofast (high better)& at -Ofast (high better) & at -Os (high better)\\\hline
400.perlbench	& 1.00  & -9120  & 544  \\\hline
401.bzip2	& 1.00  & -1600  & 128  \\\hline
403.gcc	        & 1.00  & -58176 & 3384 \\\hline
429.mcf	        & 1.03  & 160    & 16   \\\hline
433.milc	& 1.00  & -656   & 224  \\\hline
444.namd	& 1.00  & -3864  & -1168\\\hline
445.gobmk	& 0.99  & -20480 & -264 \\\hline
447.dealII	& 0.95  & -27836 & 50934\\\hline
450.soplex	& 0.99  & 2220   & 348  \\\hline
453.povray	& 0.97  & 164    & -472 \\\hline
456.hmmer	& 0.99  & -3464  & -352 \\\hline
458.sjeng	& 1.02  & 440    & 1456 \\\hline
462.libquantum	& 1.00  & -96    & 0    \\\hline
464.h264ref	& 1.00  & -3424  & 864  \\\hline
470.lbm	        & 1.00  & 0      & 0    \\\hline
471.omnetpp	& 1.00  & 2688   & 200  \\\hline
473.astar	& 1.00  & -928   & 152  \\\hline
482.sphinx3	& 0.99  & 3008   & -176 \\\hline
483.xalancbmk	& 1.01  & 46492  & 4012 \\\hline
Geomean         & 0.997 &  & \\\hline
    \end{tabular}
  \end{center}
  \caption{Execution time (ratio) and code size change (bytes) with and without
    \gcm{} (\GCM{}) on \SPEC{}: performance uplift at -Ofast in mcf and sjeng;
    code size improvement in dealII at -Os.}
  \label{tab:code-size}
\end{table}

@@

We see some nice gains in code size at -Os with \gcm{} (403.gcc, 447.dealII, and
483.xalancbmk) as shown in Table~\ref{tab:code-size}.  The code size listed here
is the text size delta (from linux size command) of the final executable for
each benchmark.  Some benchmarks like 473.astar increased in code size by almost
2\%. This is because once the code-size of a function decreases (due to \GCM{}),
it becomes cheaper to inline. As we can see in Table~\ref{tab:stats}, four more
functions got inlined in 473.astar. Except for 447.dealII, 450.soplex,
482.sphinx3 and 483.xalancbmk all other benchmarks got more functions
inlined. Also, since the pass runs early, it affects many optimizations which
rely on the number of instructions, length of the use-def chain, and other
metrics.

The code-size at -Ofast is very widespread with huge gains in 483.xalancbmk to
serious regressions in 403.gcc. This is mostly because the compiler's focus is
to improve performance at the cost of code-size at -Ofast, so passes like
inlining, loop-unrolling, code-versioning are very aggressive at -Ofast.
